Multiset-trie data structure

### 2019-02-28 tex/tex/s_intro.tex
introduction changes

Multiset data structure is usually implemented as a search tree and its elements can be accessed by a key. 
%
This approach is good when individual elements of a multiset are of interest. However, it is not as optimal for operations 
that use containment relation between multisets, also known as containment queries. 
%
Containment relation allows us to operate directly with the collections that are associated with a multiset such as a set 
of submultiset and a set of supermultisets.
%
Currently, the solution to searching or retrieval of a set of multisets using containment queries involves inverted file, 
signature tree or B+ tree~\cite{Helmer2003}. The solution provides a key-value look-up for elements of a multiset implying that 
containment operations are still element-wise.

@@

% description of innovations
%
In this paper we propose a data structure \emph{multiset-trie} that is designed for storage and 
processing of a set of multisets. It extends the \emph{set-trie} data structure proposed by 
Savnik~\cite{savnik2013index} that was designed for storage and processing of a set of sets. 
%
Set-trie is a trie based data structure that provides a fast search and retrieval of sets and implements 
set-containment operations. 
%
Multiset-trie generalizes set-trie and can work with a set of sets (as set-trie) or with 
a set of multisets providing efficient multiset-containment operations.

% intro into mstrie
The multiset-trie is an $n$-ary tree based data structure with properties similar to those of a trie. 
Multisets are associated with a collection of nodes in a tree such that every node represents an element 
of a multiset with particular multiplicity. 
%
Multiset-trie is a kind of search tree. Similarly to a trie, it uses common prefixes for shared data representation.
Unlike the compact prefix tree, the multiset-trie does not support path compression. However, the absence of path 
compression makes the multiset-trie a perfectly height-balanced tree.
%
The multiset-trie handles multisets directly by having access to each of the element 
without the need to reconstruct them for processing, which allows fast retrieval and 
containment operations. In particular, it supports submultiset and supermultiset queries.
The operations allow to find and retrieve the closest submultisets or supermultisets 
as well as to find and retrieve all of them.

>>>>

%
% problem
%
The problem we would like to address in this paper is efficient execution of containment queries on a set of multisets.
The modern implementations of data structure for a set or a multiset is usually implemented as a search tree and 
its elements can be accessed by a key. 
%
This approach is good when individual elements of a set or a multiset are of interest. However, it is not as optimal for operations 
that use containment relation between multisets. 
%
Containment relation allows us to operate directly with the collections that are associated with a multiset such as a set 
of submultiset and a set of supermultisets.
%
Currently, the solution to searching or retrieval of a set of multisets using containment queries involves inverted file, 
signature tree or B+ tree~\cite{Helmer2003}. These solutions provide a key-value look-up for elements of a multiset implying that 
containment operations are still element-wise. In order to improve the efficiency of operations we organize a set of 
multisets in a different way described further below.

@@

% description of innovations
%
In this paper we propose a data structure \emph{multiset-trie} that is designed for storage and 
processing of a finite bounded set of multisets. It extends the \emph{set-trie} data structure proposed 
by Savnik~\cite{savnik2013index} that was designed for storage and processing of a finite bounded (?or 
unbounded?) set of sets. 
%
Set-trie is a trie based data structure that provides a fast search and retrieval of sets and implements 
set-containment operations. 
%
Multiset-trie generalizes set-trie and can work with a set of sets (as set-trie) or with 
a set of multisets providing efficient multiset-containment operations.

% intro into mstrie
The multiset-trie is an $n$-ary tree based data structure with properties similar to those of a trie. 
Multisets are associated with a collection of nodes in a tree such that every node represents an element 
of a multiset with particular multiplicity bounded by a node degree $n.$
%
Multiset-trie is a kind of search tree. Similarly to a trie, it uses common prefixes for shared data representation.
Unlike the compact prefix tree, the multiset-trie does not support path compression. However, the absence of path 
compression makes the multiset-trie a perfectly height-balanced tree. Moreover, when multiset-trie is full it forms 
a complete $n$-ary tree.
%
The multiset-trie handles multisets directly by having access to each of the element 
without the need to reconstruct them for processing, which allows fast retrieval and 
containment operations. In particular, it supports submultiset and supermultiset queries.
The operations allow to find and retrieve the closest submultisets or supermultisets 
as well as to find and retrieve all of them.
